Stability and Performance of Coalitions of Prosumers Through Diversification in the Smart Grid

### 2015-11-03 Article.tex
update

{\bf Keywords:} prosumers, smart-grid, coalitions, correlation, stability 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Section I: Introduction
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}

@@

\begin{equation}
\label{epsilon_star}
\epsilon^{\star} = min_{ \epsilon \in [0,1]} \left\{ \epsilon\ s.t.\ |\Theta_{k}(G_{2}^{\epsilon})| \geq N_{COAL} \right\}
\end{equation} 
where $ G_{2}^{\epsilon} $ is the de-correlation graph $ G_{2} $ filtered by $ \epsilon $, and $ \Theta_{k}(G) $ is the set of non overlapping cliques of size k in a given graph G. In other words we select $ \epsilon^{\star} $ as the smallest threshold possible such that the filtered de-correlation graph contains at least $ N_{COAL} $ non overlapping cliques of size k. The existence of $ \epsilon^{\star} $  as defined in equation  \ref{epsilon_star} is not guaranteed. The users has indeed to provide consistent values of $ N_{COAL} $ or k compared to the size of the agent population $ \mathcal{A} $.

@@

A key point for the coalitions, besides stability and productivity, is their resilience. The resilience of a system refers to its ability to perform its tasks when subject to failures of its components. Therefore, the notion of resilience we will use in the following can be seen as the ability of the coalition structures to inject stable power in the grid when node failures occur. According to our model, the grid operator specified two thresholds ($P^{MIN}$ and $ \phi $) such that the power injected by every coalition is constrained : $ P_{S}^{CRCT} \in [P^{MIN}, P_{S}^{CRCT \star}] $. As long as a coalition can propose a contract value higher than $ P^{MIN} $, it is valid and allowed to enter the energy market. We define the resilience of a coalition S as the probability that S produces more than the $ P^{MIN} $ threshold : $ \mathcal{R}_{S} = Pr[P_{S} >= P^{MIN}] = 1 - Pr[P_{S} < P^{MIN}] $. And we extend this measure to the coalition structures :

>>>>

{\bf Keywords:} prosumers, coalition formation, correlation, stability, clique expansion, electricity market
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Section I: Introduction
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}

@@

\begin{equation}
\label{epsilon_star}
\epsilon^{\star} = min_{ \epsilon \in [0,1]} \left\{ \epsilon\ s.t.\ |\Theta_{k}(G_{2}^{\epsilon})| \geq N_{COAL} \right\}
\end{equation} 
where $ G_{2}^{\epsilon} $ is the de-correlation graph $ G_{2} $ filtered by $ \epsilon $, and $ \Theta_{k}(G) $ is the set of non overlapping cliques of size k in a given graph G. In other words we select $ \epsilon^{\star} $ as the smallest threshold possible such that the filtered de-correlation graph contains at least $ N_{COAL} $ non overlapping cliques of size k. In practice, since finding cliques requires exponential time, we use triangles \cite{Schank2001} ($k=3$ in eq. \ref{epsilon_star}) rather than cliques as soon as the number of nodes is not small. Note also that the existence of $ \epsilon^{\star} $  as defined in equation  \ref{epsilon_star} is not guaranteed. The users has indeed to provide consistent values of $ N_{COAL} $ or k compared to the size of the agent population $ \mathcal{A} $.

@@

A key point for the coalitions, besides stability and productivity, is their resilience. The resilience of a system refers to its ability to perform its tasks when subject to failures of its components. We consider here the case of random failures of the power electronics of some agents that has the consequence of preventing them from participating in the market. Therefore, the notion of resilience we will use in the following can be seen as the ability of the coalition structures to inject stable power in the grid when some of its internal agents are removed. According to our model, the grid operator specified two thresholds ($P^{MIN}$ and $ \phi $) such that the power injected by every coalition is constrained : $ P_{S}^{CRCT} \in [P^{MIN}, P_{S}^{CRCT \star}] $. As long as a coalition can propose a contract value higher than $ P^{MIN} $, it is valid and allowed to enter the energy market. We define the resilience of a coalition S as the probability that S produces more than the $ P^{MIN} $ threshold : $ \mathcal{R}_{S} = Pr[P_{S} >= P^{MIN}] = 1 - Pr[P_{S} < P^{MIN}] $. And we extend this measure to the coalition structures :
